Add Plant Functional Type (PFT) labels

### 2021-04-21 R/add_plant_functional_type.Rmd
going to manually check each taxon now compared with the NEON growth form observations

# simplify the growth form into "tree", "shrub", "saplng" etc.  
cleaned_spectra_merged <- cleaned_spectra_merged %>% 
  rowwise() %>%
  # parse out the last word in each entry's growthForm
  # make this code more efficient????? 
  mutate(growthForm_simple = rev(strsplit(growthForm, " ")[[1]])[1])

@@

```{r}
# summarize the merged growthform data
cleaned_spectra_merged %>% 
  distinct(spectraID, .keep_all = TRUE) %>% 
  group_by(genusSpecies, growthForm_simple) %>% 
    tally() 
```

>>>>

# simplify the growth form into "tree", "shrub", "sapling" etc.  
cleaned_spectra_merged <- cleaned_spectra_merged %>% 
  rowwise() %>%
  # parse out the last word in each entry's growthForm
  # make this code more efficient????? 
  mutate(growthForm_simple = rev(strsplit(growthForm, " ")[[1]])[1])

@@

```{r}
# summarize the merged growthform data
cleaned_spectra_merged %>% 
  distinct(spectraID, .keep_all = TRUE) %>% 
  group_by(genusSpecies, growthForm_simple) %>% 
    tally()

# summarize the merged growthform data
cleaned_spectra_merged %>% 
  distinct(spectraID, .keep_all = TRUE) %>% 
  # keep just the tree and shrub growth forms, remove rows with "sampling" and "liana"
  filter(growthForm_simple %in% c("tree","shrub")) %>% 
  group_by(genusSpecies, growthForm_simple) %>% 
    tally() 
```
